---
title: "r/cow's OWL Unofficial All-Rookie voting"
author: u/blankepitaph
output: pdf_document
---

# Data prep

Prep data:

```{r}
library(tidyverse)
library(ggimage)
library(rsvg)

rookies = read_tsv(
  'rookies_long.tsv', col_types = cols()
) %>% 
  mutate(points = case_when(
    selection == 'first_team' ~ 2,
    selection == 'second_team' ~ 1)
  ) 
```

Dealing with 'multi-role players' - based on playtime, I'm assigning Checkmate
as MT (most playtime on Orisa/Rein), Skewed as MS (most playtime on Brig, traditionally
an MS hero), and Aztac as FS

```{r}
rookies = rookies %>% 
  mutate(
    role = ifelse(player == 'Skewed', 'MS', role),
    role = ifelse(player == 'Checkmate', 'MT', role),
    role = ifelse(player == 'Aztac', 'FS', role)
  )
```

# Tabulating votes

## Positionless voting

```{r}
# positionless voting
rookie_votes_total = rookies %>% 
  select(-timestamp) %>% 
  
  # get sum of points
  group_by(player, team, role) %>% 
  summarise(total_points = sum(points), .groups = 'drop') %>% 
  arrange(desc(total_points)) %>% 
  rownames_to_column() # identify top 12 by eye

rookie_votes_total
```

The positionless All-Rookie First Team:
Pelican (DPS), Shy (DPS), Ga9a (MT), Piggy (OT), Kaan (FS), Mmonk (FS)

All-Rookie Second Team:
Flora (DPS), MuZe (MT), JJANGGU (MT), Vestola (OT), Skewed (MS), Nisha (MS)

## Position-based voting

```{r}
rookies_position_ranks = rookie_votes_total %>% 
  select(-rowname) %>% 
  
  # get top vote counts for each role
  group_by(role) %>% 
  mutate(rank = dense_rank(desc(total_points)))

rookies_position_ranks

# write_tsv(rookies_position_ranks, 'rookies_position_ranks.tsv')
```

The position-based All-Rookie First Team:
Pelican (DPS), Shy (DPS), Ga9a (MT), Piggy (OT), Kaan (FS), Nisha (MS)

All-Rookie Second Team:
Flora (DPS), Aspire (DPS), MuZe (MT), Vestola (OT), Mmonk (FS), Skewed (MS)

# Plots

Team color reference:

```{r}
team_colors = c(
  'ATL' = '#910F1B',
  'BOS' = '#174B97',
  'CDH' = '#FFA000',
  'FLA' = '#CF4691',
  'GZC' = '#67A2B2',
  'HOU' = '#97D700',
  'HZS' = '#FB7299',
  'LAG' = '#3C1053',
  'LAV' = '#FFD100',
  'LDN' = '#59CBE8',
  'NYXL' = '#0F57EA',
  'PAR' = '#8D042D',
  'SHD' = '#D22630',
  'TOR' = '#000000',
  'VAN' = '#2FB228',
  'WAS' = '#990034'
)
```

Create overall plot:

```{r}
overall_plot = rookies_position_ranks %>% 
  mutate(img_link = paste0('team_logos/', team, '.png')) %>% 
  filter(rank <= 7) %>% 
  mutate(role = factor(role, levels = c('DPS', 'MT', 'OT', 'FS', 'MS'))) %>% 
    
  # plot
  ggplot() +
  geom_bar(
    aes(x = reorder(player, -total_points), y = total_points, fill = team),
    stat = 'identity', color = 'black') +
  geom_image(
    aes(x = player, y = total_points + 30, image = img_link),
    size = 0.1, by = 'width', asp = 0.9) +
  facet_wrap(
    vars(role), scales = 'free_x', ncol = 5, nrow = 1) +
  coord_cartesian(
    y = c(0, 520)
  ) +
  scale_fill_manual(values = team_colors) +
  labs(
    title = "r/cow's overall All-Rookie team voting",
    subtitle = 'Based on 248 community votes - max 7 players per role shown',
    x = 'Player',
    y = 'Total points',
    caption = 'u/blankepitaph, 2021/08/19'
  ) +
  guides(
    fill = FALSE
  ) +
  theme(
    panel.border = element_rect(colour = 'black', size = 0.5, fill = NA),
    panel.background = element_blank(),
    strip.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey', linetype = 'dotted'),
    strip.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.title = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1))

overall_plot

ggsave('plots/overall.png', overall_plot, height = 5, width = 15, dpi = 'retina')
    
```

DPS only plot:

```{r}
dps_plot = rookies_position_ranks %>% 
  mutate(img_link = paste0('team_logos/', team, '.png')) %>% 
  filter(role == 'DPS') %>% 
    
  # plot
  ggplot() +
  geom_bar(
    aes(x = reorder(player, -total_points), y = total_points, fill = team),
    stat = 'identity', color = 'black') +
  geom_image(
    aes(x = player, y = total_points + 30, image = img_link),
    size = 0.05, by = 'width', asp = 2) +
  coord_cartesian(
    y = c(0, 520)
  ) +
  scale_fill_manual(values = team_colors) +
  labs(
    title = '2021 Rookie DPS players',
    x = 'Player',
    y = 'Total points',
    caption = 'u/blankepitaph, 2021/08/19'
  ) +
  guides(
    fill = FALSE
  ) +
  theme(
    panel.border = element_rect(colour = 'black', size = 0.5, fill = NA),
    panel.background = element_blank(),
    strip.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey', linetype = 'dotted'),
    strip.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.title = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1))

dps_plot

ggsave('plots/dps_all.png', dps_plot, height = 5, width = 8, dpi = 'retina')
```

Tank only plot:

```{r}
tank_plot = rookies_position_ranks %>% 
  mutate(img_link = paste0('team_logos/', team, '.png')) %>% 
  filter(role %in% c('MT', 'OT')) %>% 
  mutate(role = factor(role, levels = c('MT', 'OT'))) %>% 
    
  # plot
  ggplot() +
  geom_bar(
    aes(x = reorder(player, -total_points), y = total_points, fill = team),
    stat = 'identity', color = 'black') +
  geom_image(
    aes(x = player, y = total_points + 30, image = img_link),
    size = 0.1, by = 'width', asp = 1.1) +
  facet_wrap(
    vars(role), scales = 'free_x', ncol = 5, nrow = 1) +
  coord_cartesian(
    y = c(0, 520)
  ) +
  scale_fill_manual(values = team_colors) +
  labs(
    title = '2021 Rookie Tank players',
    x = 'Player',
    y = 'Total points',
    caption = 'u/blankepitaph, 2021/08/19'
  ) +
  guides(
    fill = FALSE
  ) +
  theme(
    panel.border = element_rect(colour = 'black', size = 0.5, fill = NA),
    panel.background = element_blank(),
    strip.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey', linetype = 'dotted'),
    strip.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.title = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1))

tank_plot

ggsave('plots/tank_all.png', tank_plot, height = 5, width = 8, dpi = 'retina')
```

Support only plot:

```{r}
support_plot = rookies_position_ranks %>% 
  mutate(img_link = paste0('team_logos/', team, '.png')) %>% 
  filter(role %in% c('FS', 'MS')) %>% 
  mutate(role = factor(role, levels = c('FS', 'MS'))) %>% 
    
  # plot
  ggplot() +
  geom_bar(
    aes(x = reorder(player, -total_points), y = total_points, fill = team),
    stat = 'identity', color = 'black') +
  geom_image(
    aes(x = player, y = total_points + 30, image = img_link),
    size = 0.1, by = 'width', asp = 1.1) +
  facet_wrap(
    vars(role), scales = 'free_x', ncol = 5, nrow = 1) +
  coord_cartesian(
    y = c(0, 520)
  ) +
  scale_fill_manual(values = team_colors) +
  labs(
    title = '2021 Rookie Support players',
    x = 'Player',
    y = 'Total points',
    caption = 'u/blankepitaph, 2021/08/19'
  ) +
  guides(
    fill = FALSE
  ) +
  theme(
    panel.border = element_rect(colour = 'black', size = 0.5, fill = NA),
    panel.background = element_blank(),
    strip.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey', linetype = 'dotted'),
    strip.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.title = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text = element_text(family = 'Helvetica', colour = 'black', size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1))

support_plot

ggsave('plots/support_all.png', support_plot, height = 5, width = 8, dpi = 'retina')

```

